A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

(2) We have carefully considered and followed all the comments and suggestions related to the clarity of the writing, and made the new material a thoroughly revised manuscript.

% 消融实验
(3) We have added a new experiment to attack in the YCbCr color space to reduce the perceptibility of the pereturbations.

% % 消融实验
% (4) We have used a new way to generate the fake trajectory.

% 消融实验：噪声攻击。
(4) We have added a new experiment to evaluate the attack performance of random gaussian noises.

@@

%%%% 问题 2.1 %%%%
\textit{However, there are some concerns over the implementation, performance and writing. 1. The authors state that training with Ep. 4 leads to an obvious patch on the images while using Eq.5 into the training process results in a less obvious patch. The reviewer considers that giving a constraint (e.g. $l_{\infty}$) on the $p_x$ in Eq.4 can make the perturbation imperceptible intuitively. Please give more analysis on this setting.
Besides, the reviewer hopes to know the reason why give an extra perturbation on the template region. The perturbations on template and search regions look similar, while the authors say that they are different. Please state the difference between the patch application operator on search examples and the operator on template examples.
In addition, the denotations of $A_{paste}$ in Eq.4 and $A_{add}$ in Eq.5 seem like the same one.
}

\textbf{
Thanks for the good comment.
Before analysis if giving constraint (e.g. $L_{\infty}$) on the $p_x$ in Eq.4 is really lead to imperceptible or not, let us first clarify the concept of the $A_{paste}$ and $A_{add}$, which is not tell good in the previous manuscript.}

\textbf{% 解释paste（说明不需要加 constraint）
$A_{paste}$ means that,
% we use the pixel value in in every place of the perturbation to replace the original image pixel value at the corresponding position.
% The final pixel value is changed from the original value to a new value.
in the region where the perturbation is pasted, the pixel values of the original image is replaced with the pixel values of the perturbation.
% 说明加了约束也没用。
% As a result, even though we add constraint to the perturbation and it is small, when we paste it to the image, it shows nearly black but not imperceptible.
Thus, even if we add constraints to the patch so that the perturbation values are small, when the patch is pasted to the image, it will look like an almost black region, which is obvious rather than imperceptible.
}

% 解释加法
\textbf{
The operator $A_{add}$ means to apply additive noises, where the injecting small perturbations into the image. Often need constraint. the injected noises are small and sometimes invisible. If we add a patch onto the image, the final pixel value is the original value plus a new value.}

@@

\textbf{The operator $A_{\text{add}}(\textbf{x}, p_\textbf{x}, b^{fake}_{\textbf{x}})$ and $\textbf{z} + \delta_\textbf{z}$ is similar. The only difference is that, $A_{\text{add}}$ means add the perturbation to a specific region because the patch size is less than the image, while $+$ means add the perturbation to the full image because the size is the same.}

\textbf{For your convenience of cross checking, the new added text is shown as follows:}

\uline{
$A_{paste}$ means that, in the region where the perturbation is pasted, the pixel values of the original image is replaced with the pixel values of the perturbation.
% 解释加法
The operator $A_{add}$ means to apply additive noises, where the injecting small perturbations into the input samples. Often need constraint. the injected noises are small and sometimes invisible.  
}

@@

\begin{table}[]
  \centering
  \caption{Attack performance when only use the template/search perturbation.}
  \label{table:one_branch}
  \begin{tabular}{@{}rcccc@{}}
  \toprule
                & \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\
                & AO                & SR                & AO               & SR               \\ \midrule
  Only Template & 0.510             & 0.567             & 0.156            & 0.106            \\
  Only Search   & 0.714             & 0.841             & 0.160            & 0.132            \\
  Both          & 0.153             & 0.123             & 0.840            & 0.890            \\
  \bottomrule
  \end{tabular}
\end{table}

%%%% 问题 2.4 %%%%
\textit{4. As reviewer 1 and reviewer 2 say, the perturbations added to template regions and research regions are not imperceptible, which may be helpful to misguide the tracker. The reviewer considers that adding a similar random pattern on the template and search regions to further illustrate the effectiveness of the proposed method.}

\textbf{To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions: the mean value and standard deviation is the same as the template/search image.
For your convenience in cross-checking, the new text is given as follows.
}

\begin{table}[t]
  \centering
  \caption{Attack performance using the gaussian random noises. The mean value is set to zero. The standard deviation (std) is changed from 0.1 to 100.0. The noises are added to both the template and the search image, position and size is the same of original setting. The experiment is performed on GOT-Val.}
  \begin{tabular}{@{}rccccc@{}}
  \toprule
  \multirow{2}{*}[-2pt]{std} & \multirow{2}{*}[-2pt]{SSIM}& \multicolumn{2}{c}{Untargeted Attack} & \multicolumn{2}{c}{Targeted Attack} \\ \cmidrule{3-6}
                             &                            & AO                & SR                & AO               & SR               \\ \midrule
  1.0                        & 0.98                       & 0.760             & 0.896             & 0.142            & 0.101            \\
  10.0                       & 0.38                       & 0.761             & 0.898             & 0.143            & 0.102            \\
  100.0                      & 0.01                       & 0.715             & 0.850             & 0.152            & 0.112            \\ \bottomrule        
  \end{tabular}
  \label{table:noise}
\end{table}

\uline{\textit{Ablation Study: Attack performance of the random noises} To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions: the mean value and standard deviation is the same as the template/search image. Attack performance using the gaussian random noises. The mean value is set to zero. The noises are added to both the template and the search image, position and size is the same of original setting. We not train.
% 实验结果的分析
As shown in Table \ref{table:noise}, if we add small or midiam noises, it will not the tracking performance. Only very large pattern will have affact, but the SSIM is evry small.
}

### 2021-09-15 博士/论文提交/adversarial_attack/TCSVT/大修/正文/main.tex
写response

%\uline{
To overcome all the shortcomings of the above methods, we propose to train a translucent perturbation $\delta$ for the template image $\textbf z$, and a translucent patch $p$ for the search image $\textbf x$. 
%}
After adding $\delta$ to $\textbf z$ and adding the fake target $p$ into $\textbf x$, the tracker outputs the location and size of the adversarial patch instead of the real target (see Figure \ref{fig:net}). Both $\delta$ and $p$ are universal (\ie, video-agnostic), which means perturbing a novel video only involves the mere addition of the perturbations to the template and search images -- and does not require gradient optimization or network inference.
\begin{equation}
  \begin{gathered}
    \min\limits_{\delta_\textbf{x}, \delta_\textbf{z}} \mathop{\mathbb{E}}\limits_{(\textbf{x}, \textbf{z}, y^{fake})} L(y^{fake}, f(A_{\text{add}}(\textbf{x}, p_\textbf{x}, b^{fake}_{\textbf{x}}), \textbf{z} + \delta_\textbf{z}))\\
    \text{s.t.}\ ||\delta_\textbf{x}||_p \le \epsilon_1, ||\delta_\textbf{z}||_p \le \epsilon_2,
  \end{gathered}
\end{equation}
where $A_{\text{add}}$ is a patch application operator which adds the patch into the search image according to $b^{fake}_{\textbf{x}}$.
\uline{The operator $A_{add}$ means to apply additive noise, where the injecting small perturbations into the input samples. Often need constraint. the injected noise are small and sometimes invisible.}

@@

\uline{\textit{Ablation Study: Attack performance of the random noise} To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions: the mean value and standard deviation is the same as the template/search image. Attack performance using the gaussian random noise. The mean value is set to zero. The noise is added to both the template and the search image, position and size is the same of original setting. We not train.
% 实验结果的分析
As shown in Table \ref{table:noise}, if we add small or midiam noise, it will not the tracking performance. Only very large pattern will have affact, but the SSIM is evry small.
}

>>>>

%\uline{
To overcome all the shortcomings of the above methods, we propose to train a translucent perturbation $\delta$ for the template image $\textbf z$, and a translucent patch $p$ for the search image $\textbf x$. 
%}
After adding $\delta$ to $\textbf z$ and adding the fake target $p$ into $\textbf x$, the tracker outputs the location and size of the adversarial patch instead of the real target (see Figure \ref{fig:net}). Both $\delta$ and $p$ are universal (\ie, video-agnostic), which means perturbing a novel video only involves the mere addition of the perturbations to the template and search images -- and does not require gradient optimization or network inference.
\begin{equation}
  \begin{gathered}
    \min\limits_{\delta_\textbf{x}, \delta_\textbf{z}} \mathop{\mathbb{E}}\limits_{(\textbf{x}, \textbf{z}, y^{fake})} L(y^{fake}, f(A_{\text{add}}(\textbf{x}, p_\textbf{x}, b^{fake}_{\textbf{x}}), \textbf{z} + \delta_\textbf{z}))\\
    \text{s.t.}\ ||\delta_\textbf{x}||_p \le \epsilon_1, ||\delta_\textbf{z}||_p \le \epsilon_2,
  \end{gathered}
\end{equation}
where $A_{\text{add}}$ is a patch application operator which adds the patch into the search image according to $b^{fake}_{\textbf{x}}$.
\uline{The operator $A_{add}$ means to apply additive noises, where the injecting small perturbations into the input samples. Often need constraint. the injected noises are small and sometimes invisible.}

@@

\uline{\textit{Ablation Study: Attack performance of the random noises} To illustrate the effectiveness of the proposed method, we add a random pattern on the template and search regions: the mean value and standard deviation is the same as the template/search image. Attack performance using the gaussian random noises. The mean value is set to zero. The noises are added to both the template and the search image, position and size is the same of original setting. We not train.
% 实验结果的分析
As shown in Table \ref{table:noise}, if we add small or midiam noises, it will not the tracking performance. Only very large pattern will have affact, but the SSIM is evry small.
}
